Empirical normative theories

### 2020-08-03 simple.tex
Got rid of spurious proofs (and minor improvements)

\section{Additive single-answer empirical theories}
\subsection{Definition}
An empirical theory for a normative theory is a tuple $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$,
with ${\gleadsto} \subseteq \allargs × \Phi$, 
${\gbeats} \subseteq \allargs × \allargs$ and is irreflexive,
${\dbeats} \subseteq \alldargs × \allargs$ and is injective and its range includes $\gbeatsinv(\allargs)$ (thus $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton). 
Define $\df: \allargs → \powersetz{\allargs}$ as $\df = \dbeatsinv \circ \gbeatsinv$.
Given $\ar \in \allargs$, $\df(\ar)$ denotes the \emph{fragments defending $\ar$}. 
In other words, given $\ard \in \dargs$ and $\ar_0 \in \allargs$, $\ar_2 \in \df(\ar_0)$ iff $\exists \ar_1 \in \allargs \suchthat \ar_2 \dbeats \ar_1 \gbeats \ar_0$.
A \emph{coalition defending $\ar$} is any element of $\powersetz{\df(\ar)}$.
The symbol $+$ in an empirical theory stands for a function $+: \bigcup_{\ar \in \allargs}(\set{s} × \powersetz{\df(\ar)}) → \allargs$.
Given any $\ar \in \allargs$ and $\emptyset ≠ \dargs \subseteq \df(\ar)$, $\ar + \dargs$ means $+(\ar, \dargs)$. 
Given any $\ar \in \allargs$, define $\dfp(\ar)$, the \emph{defenders of $\ar$}, as $\dfp(\ar) = \set{\ar + \dargs \suchthat \emptyset ≠ \dargs \subseteq \df(\ar)}$.

@@

Given $i \in I, \phi \in \Phi, \ar \in \allargs$ and $\args \subseteq \gbeatsinv(\ar)$, define $\args \ibeats \ar$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar) \cap \hist \land \ar \in \histend \land \hist \nileadstost \phi$. (The striked through $\phi$ in superscript is there to suggest that, intuitively, $\args$ argue against $\phi$, from the point of view of $i$.)

Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the $\di(\ar) \subseteq \powersetz{\alldargs}$ as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \land \args \ibeats \ar}$. It represents the coalitions of fragments required to defend $\ar$ (when arguing for $\phi$) from the point of view of $i$. 
The following proposition shows that these coalitions can be added to $\ar$, and will be useful for other results.
\begin{proposition}
	$\dargs \in \di(\ar) ⇒ \emptyset ≠ \dargs \subseteq \df(\ar)$.
\end{proposition}
\begin{proof}
	Let us prove that $\set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar)} = \powersetz{\df(\ar)}$, from which the conclusion follows, and which can be useful to clarify the relationship between $\di(\ar)$ and $\df(\ar)$.

	First (from left to right), $\forall \args \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0): \dargs = \dbeatsinv(\args) \in \powersetz{(\dbeatsinv \circ \gbeatsinv)(\ar)}$. 
	Indeed, as $\args ≠ \emptyset$, we can pick some $\ar_1 \in \args$, and $\ar_1 \gbeats \ar_0$, hence, for some $\ard \in \alldargs$, $\ard \dbeats \ar_1$ (as mandated by ${\dbeats}$), thus $\ard \in \dargs$, hence $\dargs ≠ \emptyset$. Also, picking any $\ard \in \dargs$, we see that for some $\ar_1 \in \args$, $\ard \dbeats \ar_1 \gbeats \ar_0$.

	Second (from right to left), $\dargs \in \powersetz{(\dbeatsinv \circ \gbeatsinv)(\ar)} ⇒ \exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \suchthat \dbeatsinv(\args) = \dargs$. 
	Defining $\args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar_0)$, we see that $\dbeatsinv(\args) = \dargs$: considering any $\ard \in \dargs$, $\ard \dbeats \ar_1 \gbeats \ar_0$ for some $\ar_1 \in \allargs$, thus, $\ar_1 \in \args$, thus, $\ard \in \dbeatsinv(\args)$; and considering any $\ard \in \dbeatsinv(\args)$, $\ard \dbeats \ar_1 \in \args$, $\ar_1 \gbeats \ar_0$, thus, $\ard \in \dargs$ \commentOC{This is incorrect.}. 
	That $\args ≠ \emptyset$ follows from $\dargs ≠ \emptyset$.
\end{proof}

Observe that $\di(\ar) \subseteq \df(\ar)$.
Define $\dip \subseteq \allargs × \allargs$ as $\dip(\ar) = \set{(\ar + \dargs) \suchthat \dargs \in \di(\ar)}$.
Given $i \in I, \phi \in \gPhi$, define $\gargs \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\phi))$.

@@

\begin{definition}[Convincingness]
	$\forall i \in I, \phi \in \gPhi, \ar \in \gargs: \ar$ $i$-defends $\phi$.
\end{definition}

>>>>

\section{Additive single-answer empirical theories}
\subsection{Definition}
An empirical theory for a normative theory is a tuple $(\gleadsto, \gbeats, \alldargs, \dbeats, +)$,
with ${\gleadsto} \subseteq \allargs × \Phi$, 
${\gbeats} \subseteq \allargs × \allargs$ and is irreflexive,
${\dbeats} \subseteq \alldargs × \allargs$ and is injective and its range includes $\gbeatsinv(\allargs)$ (thus $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton). 
Define $\df: \allargs → \powersetz{\allargs}$ as $\df = \dbeatsinv \circ \gbeatsinv$.
Given $\ar \in \allargs$, $\df(\ar)$ denotes the \emph{fragments defending $\ar$}. 
In other words, given $\ard \in \dargs$ and $\ar_0 \in \allargs$, $\ard \in \df(\ar_0)$ iff $\exists \ar_1 \in \allargs \suchthat \ard \dbeats \ar_1 \gbeats \ar_0$.
A \emph{coalition defending $\ar$} is any element of $\powersetz{\df(\ar)}$.
The symbol $+$ in an empirical theory stands for a function $+: \bigcup_{\ar \in \allargs}(\set{s} × \powersetz{\df(\ar)}) → \allargs$.
Given any $\ar \in \allargs$ and $\emptyset ≠ \dargs \subseteq \df(\ar)$, $\ar + \dargs$ means $+(\ar, \dargs)$. 
Given any $\ar \in \allargs$, define $\dfp(\ar)$, the \emph{defenders of $\ar$}, as $\dfp(\ar) = \set{\ar + \dargs \suchthat \emptyset ≠ \dargs \subseteq \df(\ar)}$.

@@

Given $i \in I, \phi \in \Phi, \ar \in \allargs$ and $\args \subseteq \gbeatsinv(\ar)$, define $\args \ibeats \ar$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar) \cap \hist \land \ar \in \histend \land \hist \nileadstost \phi$. (The notation uses a striked through $\phi$ in superscript to suggest that when $\args \ibeats \ar$, the coalition $\args$ argues against $\phi$, from the point of view of $i$.)

Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the $\di(\ar) \subseteq \powersetz{\alldargs}$ as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \land \args \ibeats \ar}$. It represents the coalitions of fragments required to defend $\ar$ (when arguing for $\phi$) from the point of view of $i$. 
The following proposition shows that these coalitions can be added to $\ar$, and will be useful for other results.
\begin{proposition}
	$\forall i \in I, \phi \in \gPhi, \ar \in \allargs: \dargs \in \di(\ar) ⇒ \emptyset ≠ \dargs \subseteq \df(\ar)$.
\end{proposition}
\begin{proof}
	Let us prove that $\forall \ar \in \allargs: \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar)} = \powersetz{\df(\ar)}$, from which the conclusion follows, and which can be useful to clarify the relationship between $\di(\ar)$ and $\df(\ar)$. Note that by definition of $\df(\ar)$, $\dargs \in \powersetz{\df(\ar)}$ iff $\emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar))$. 
	Thus, we have to prove that
	$\forall \dargs \subseteq \allargs$:
	\begin{equation}
		\exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \suchthat \dbeatsinv(\args) = \dargs ⇔ \emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar)).
	\end{equation}

	First (from left to right), given any $\args \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \land \dargs = \dbeatsinv(\args)$, let us show that $\dargs ≠ \emptyset$ and that $\dargs \subseteq \dbeatsinv(\gbeatsinv(\ar))$. 
	Indeed, as $\args ≠ \emptyset$, we can pick some $\ar_1 \in \args$, from which follows that $\ar_1 \gbeats \ar_0$, hence, for some $\ard \in \alldargs$, $\ard \dbeats \ar_1$ (as mandated by ${\dbeats}$), thus $\ard \in \dargs$, hence $\dargs ≠ \emptyset$. Also, because $\args \subseteq \gbeatsinv(\ar)$, $\dbeatsinv(\args) \subseteq \dbeatsinv(\gbeatsinv(\ar))$.

	Second (from right to left), let us show that $\emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar)) ⇒ \exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \suchthat \dbeatsinv(\args) = \dargs$. 
	Defining $\args = {\dbeats}(\dargs) \cap \gbeatsinv(\ar_0)$, we see that $\dbeatsinv(\args) = \dargs$: considering any $\ard \in \dargs$, $\ard \dbeats \ar_1 \gbeats \ar_0$ for some $\ar_1 \in \allargs$, thus, $\ar_1 \in \args$, thus, $\ard \in \dbeatsinv(\args)$; and considering any $\ar' \in \dbeatsinv(\args)$, $\ar' \dbeats \ar_1$ for some $\ar_1 \in \args$, thus $\ar_1 \gbeats \ar_0$, thus, $\ar_1 \in {\dbeats}(\dargs)$, thus $\ard \dbeats \ar_1$ for some $\ard \in \dargs$, and by injectivity  of $\dargs$, $\ar' = \ard$, whence $\ar' \in \dargs$. 
	That $\args ≠ \emptyset$ follows from $\dargs ≠ \emptyset$.
\end{proof}

Given $\ar \in \allargs$, define $\dip(\ar) = \set{(\ar + \dargs) \suchthat \dargs \in \di(\ar)}$, representing the subset of defenders of $\ar$ useful for proving $\phi$ from the point of view of $i$.
Given $i \in I, \phi \in \gPhi$, define $\gargs \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\phi))$.

@@

\begin{definition}[Convincingness]
	An empirical theory is \emph{convincing} iff $\forall i \in I, \phi \in \gPhi, \ar \in \gargs: \ar$ $i$-defends $\phi$.
\end{definition}
